Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Consistent hyphenation for 0-CFA

A common technique to accelerate convergence in flow analyses is to share a
common, global store.
%
To retain soundness, this store grows monotonically.
%
Formally, we can cast this optimization as a second abstraction or as the
application of a widening operator during the fixed-point iteration.
%
In the ISWIM language, such a widening makes 0CFA quartic in the size of the
program.
%
Thus, in one step, complexity drops from intractable exponentiality to merely
daunting polynomiality.

@@

[Computes results more like Earl, et al.'s 0CFA, which times out on
  the Church numeral benchmark and so even though it offers a fair
  point of comparison, a more thorough evaluation is likely to
  uninformative as the other benchmarks are highly likely to timeout
  as well (and it would require significant effort to extend their
  implementation with the features needed to analyze our benchmark
  suite).  That implementation is evaluated against much smaller
  benchmarks: the largest program consists of 63 \emph{subexpressions}
  and times out after 30 minutes.]

Vardoulakis and Shivers evaluate their CFA2
analyzer~\cite{dvanhorn:Vardoulakis2011CFA2} against a variant of 0CFA
defined in their framework.  [NEED TIMING FOR 0CFA ON CHURCH.]  The
Church example is the largest benchmark Vardoulakis and Shivers
consider.  More work would be required to scale the analyzer to the
set of features required by our benchmarks.

>>>>

A common technique to accelerate convergence in flow analyses is to share a
common, global store.
%
To retain soundness, this store grows monotonically.
%
Formally, we can cast this optimization as a second abstraction or as the
application of a widening operator during the fixed-point iteration.
%
In the ISWIM language, such a widening makes 0-CFA quartic in the size of the
program.
%
Thus, in one step, complexity drops from intractable exponentiality to merely
daunting polynomiality.

@@

[Computes results more like Earl, et al.'s 0-CFA, which times out on
  the Church numeral benchmark and so even though it offers a fair
  point of comparison, a more thorough evaluation is likely to
  uninformative as the other benchmarks are highly likely to timeout
  as well (and it would require significant effort to extend their
  implementation with the features needed to analyze our benchmark
  suite).  That implementation is evaluated against much smaller
  benchmarks: the largest program consists of 63 \emph{subexpressions}
  and times out after 30 minutes.]

Vardoulakis and Shivers evaluate their CFA2
analyzer~\cite{dvanhorn:Vardoulakis2011CFA2} against a variant of 0-CFA
defined in their framework.  [NEED TIMING FOR 0-CFA ON CHURCH.]  The
Church example is the largest benchmark Vardoulakis and Shivers
consider.  More work would be required to scale the analyzer to the
set of features required by our benchmarks.
